Multivariate Skew-Normal Mixture Model for Infant Development Clustering

### 2019-05-30 poster/poster.tex
poster

\begin{table}[]
\caption{\label{tab:unnamed-chunk-4}Estimated effects of sex and race on odds of cluster membership relative to the reference cluster.}
\centering
\begin{tabular}{lll}
\hline
Variable & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 2\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 3\\ $\hat{\text{OR}}$ (95\% CrI)\end{tabular}} \\ \hline
(B,F)  & 0.87 (0.62, 1.16) & 0.91 (0.68, 1.22) \\
(W,M)  & 1.12 (0.80, 1.68) & 1.04 (0.70, 1.55) \\
(W,F) & 0.79 (0.53, 1.14) & 1.81 (1.54, 2.20) \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[]
\caption{\label{tab:unnamed-chunk-4}Estimated effects of sex and race on odds of cluster membership relative to the reference cluster.}
\centering
\begin{tabular}{lll}
\hline
Variable & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 2\\ $\hat{\text{O}}$ (95\% CrI)\end{tabular}} & \multicolumn{1}{c}{\begin{tabular}[c]{@{}c@{}}Class 3\\ $\hat{\text{O}}$ (95\% CrI)\end{tabular}} \\ \hline
(B,F)  & 0.87 (0.62, 1.16) & 0.91 (0.68, 1.22) \\
(W,M)  & 1.12 (0.80, 1.68) & 1.04 (0.70, 1.55) \\
(W,F) & 0.79 (0.53, 1.14) & 1.81 (1.54, 2.20) \\ \hline
\end{tabular}
\end{table}
